---
title: "Issue 150 Interview Question"
author: "Joshua de la Bruere"
date: "6/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## This week’s question:
Given string S, print the longest subsequence from S that contains alternating vowels and consonants. If multiple such subsequences exist having the same length, print the subsequence with the maximum sum of ASCII values of its characters.

### Example:

```
$ alternateChars(‘ababab’)
$ ‘ababab’
```

```
$ alternateChars(‘cassidyisanerd’)
$ ‘casiyisaner’
```
  
## My Process. 

I'm not actually familiar with a function in R that can determine if a letter is a vowel or consonant. 

I think the easiest approach to writing my own function that does this is to make a list of vowels. I'm only going to be using lower case values as nothing in the prompt implies that I have to have both cases. 

The function here will just check if the character is in this list of strings. 

```{r}

library(tidyverse) #This could be done is base, but I really really like piping
 
is_vowel <-  function(letter){
  

  # Tests
  if(typeof(letter) != "character"){
    warning("The provided string was not a character\n")
    return(NULL)
  }
  #send to lowercase
  letter <- tolower(letter)
  
  
  if(nchar(letter) != 1){
    warning("The length of string was > 1\n")
    return(NULL)
  }
  
  isletter <- ifelse(letter %in% letters, "No", stop("Non letter character provided"))
  
  list_of_letters <- c("a", "e", "i", "o", "u")
  
  val <-  ifelse (letter %in% list_of_letters, TRUE, FALSE)
  return(val)
  }

is_vowel("R")
is_vowel("a")
is_vowel("t")
is_vowel("E")
is_vowel(F)
is_vowel("test")
is_vowel("1")

```
You can see how I test the function to make sure it's working for a few cases. I added a few helpful warning messages, and cases where the function should return a null value.

I think the next step I want to do is to `strsplit()` any given text into individual characters. I'm pretty sure that strsplit returns a list, but I want to double check that. 

```{r}
typeof(strsplit("test", split=""))

```
It does return a list which means I could use `lapply()` to apply my `is_vowel()` function to the list 

```{r}
string_test <- strsplit("test", split="")

lapply(string_test, is_vowel)
```
I'd forgotten how `lapply()` works with if statements in functions. It's only checking the first entry on the list.  I may need to adjust my code at some point. I don't think this will be too much of an issue as I'll be validating my responses in my main function, but it's worth keeping in mine. 

```{r}
```


```{r}
ascii_sum <- function(string){
  sum(utf8ToInt(string))
}


alternateChars <- function(word){
  if(typeof(word) != "character"){
    stop("The provided value was not a character\n")
  }
  string <- tibble(word_char=unlist(strsplit(word, split=""))) %>%
    mutate(row_id = row_number(), 
           vowel_status= is_vowel(word_char)) %>%
    mutate(restart = ifelse(vowel_status != lag(vowel_status),  FALSE, TRUE), 
           restart = replace_na(restart, FALSE))
  
  
  string2 <- string %>%
    filter(restart == TRUE) %>%
    transmute(
      sub_pattern = word,
      start_row = lag (row_id),
      start_row = replace_na(start_row,1), 
      end_row = row_id-1,
      length = row_id - start_row
      
    ) %>%
    mutate(sub_pattern = str_sub(sub_pattern, start = start_row, end = end_row))%>% 
    filter(length == max(length)) 

  if(length(string2$length) > 1){
    string3 <- string2 %>%
      rowwise() %>%
    mutate(ascii_val = ascii_sum(sub_pattern)) %>%
      arrange(desc(ascii_val))
    
    longest_pattern = string3$sub_pattern[1]
  }
  else if(length(string2$length) == 0){
    longest_pattern = word

  }
  else{
    longest_pattern = string2$sub_pattern[1]
  }
  
  return(longest_pattern)
}

test <- alternateChars("wordorororodd")
alternateChars("azazazazazazazaz")
alternateChars("wordwozd")
alternateChars("1.32") # Should Break
```


This appears to be working, but I do have a few warnings I don't like to see. I think this will require a refactor of the if statements I used previously in `is_vowel()`
